Analysis 19.04.2023

### 2023-04-24 02_paper/02_study/02_fitbit paper/analysis_190423.Rmd
update analysis

table_data <- 
  df_regression %>% 
  split(.$Phase) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .
       )
      ) %>%
  map(~ tibble(time_span = names(.),
               intercept = fixef(.)[[1]],
               intercept_sd = VarCorr(.) %>% as_tibble() %>% .[1,5],
               intercept_p = coef(summary(.))[1, 5],
               slope = fixef(.)[[2]],
               slope_sd = VarCorr(.) %>% as_tibble() %>% .[2,5],
               slope_p = coef(summary(.))[2, 5]
               )
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = round(intercept, digits = 3),
            `SD(Intercept)` = round(intercept_sd$sdcor, digits = 3),
            `p-Value (Intercept)` = round(intercept_p, digits = 3),
            `Mean(Slope)` = round(slope, digits = 3),
            `SD(Slope)` = round(slope_sd$sdcor, digits = 3),
            `p-Value (Slope)` = round(slope_p, digits = 3)
            )

@@

t.test(df_test$intercept[df_test$time_span == "teaching"],
       df_test$intercept[df_test$time_span == "interview"],
       paired = TRUE)
```

@@

```{r}
CohenD(x = df_test$intercept[df_test$time_span == "teaching"],
       y = df_test$intercept[df_test$time_span == "interview"],
       pooled = T
       )
```

@@

>>>>

table_data <- 
  df_regression %>% 
#  mutate(time = time * 60) %>% 
  split(.$Phase) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .
       )
      ) %>%
  map(~ tibble(time_span = names(.),
               intercept = fixef(.)[[1]],
               intercept_sd = VarCorr(.) %>% as_tibble() %>% .[1,5],
               intercept_p = coef(summary(.))[1, 5],
               slope = fixef(.)[[2]],
               slope_sd = VarCorr(.) %>% as_tibble() %>% .[2,5],
               slope_p = coef(summary(.))[2, 5]
               )
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = round(intercept, digits = 3),
            `SD(Intercept)` = round(intercept_sd$sdcor, digits = 3),
            `p-Value (Intercept)` = round(intercept_p, digits = 3),
            `Mean(Slope)` = round(slope, digits = 3),
            `SD(Slope)` = round(slope_sd$sdcor, digits = 3),
            `p-Value (Slope)` = round(slope_p, digits = 3)
            )

@@

t.test(df_test$intercept[df_test$time_span == "teaching"],
       df_test$intercept[df_test$time_span == "interview"],
       paired = TRUE)

t.test(df_test$intercept[df_test$time_span == "teaching"],
       df_test$intercept[df_test$time_span == "end"],
       paired = TRUE)
```

@@

```{r}
CohenD(x = df_test$intercept[df_test$time_span == "teaching"],
       y = df_test$intercept[df_test$time_span == "interview"],
       pooled = T
       )

CohenD(x = df_test$intercept[df_test$time_span == "teaching"],
       y = df_test$intercept[df_test$time_span == "end"],
       pooled = T
       )
```

@@

```{r}

loess_plot_overall <-
  main %>% 
  filter(time_span == "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate_std
                       )
         ) +
  # geom_point(alpha = 0.05) + 
  geom_smooth(se = FALSE,
              size = 0.5,
              colour = "black") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0, NA),
                     breaks = seq(0, 9000, 600)) +
  scale_y_continuous(breaks = seq(-1, 1, 0.5)) + 
  labs(x = "Time (in Seconds)",
       y = "") +
  ggtitle("Overall Course of Average Heartrate") +
  theme_apa() + 
  theme(axis.title.y = element_blank())
```

t-Test mit Mittelwerten -> teaching vs. interview & teaching vs. end & interview vs. end
